Attrition in Online Learning: Understanding Persistence and Dropout in Massive Open Online Courses

### 2014-10-29 paper_v1.Rnw
added results of factor analysis

Report results of factor analysis here.

>>>>

To investigate the underlying factor structure of the reported reasons for disengaging, we conducted an exploratory factor analysis. The optimal number of factors was determined by the parallel analysis criterion and corresponding scree plot. The following five factors emerged: first, general time issues (course requires too much time; can't keep up with deadlines); second, late start (starting course late); third, difficulty (too advanced, exam too difficult); fourth, format and content (didn't enjoy online format, confusing videos, materials not explained well), and fifth, expectations (only exploring, learned all I wanted, not what I'm looking for, not challenging, credential not valuable). Only the technical difficulties item failed to load onto any factor.
